---
title: "Ch.3 Hw1 Problem 9"
output: html_document
date: "2023-09-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("ISLR")
library(ISLR)
```

```{r}
head(Auto)
```


a.) Scatterplot Matrix
```{r}
pairs(Auto[,-which(names(Auto) == "name")])
```


b.) Compute the Matrix of Correlations 
```{r}

corr_matrix = cor(Auto[,-which(names(Auto) == "name")])
print(corr_matrix)


```


c.) Multiple Linear Regression 
```{r}
# multiple linear regression model
lm_model = lm(mpg ~ . - name, data = Auto)

#Now lets display the summary 
summary(lm_model)
```
i. Is there a relationship between the predictors and the re- sponse?
ii. Which predictors appear to have a statistically significant relationship to the response?
iii. What does the coefficient for the year variable suggest?


d.) Diagnostic Plots 
```{r}
#diagnostic plots
par(mfrow=c(2,2))
plot(lm_model)

```


e.) Interaction Effects

```{r}
# Fit the model
lm_interactions = lm(mpg ~ (.-name)^2, data = Auto)

#Now let's display the summary 
summary(lm_interactions)
```

f.) Transformation of Variables

```{r}
#  different transformations and fit the model
lm_log <- lm(mpg ~ log(displacement) + log(horsepower) + log(weight), data = Auto)
summary(lm_log)

lm_sqrt <- lm(mpg ~ sqrt(displacement) + sqrt(horsepower) + sqrt(weight), data = Auto)
summary(lm_sqrt)


lm_square <- lm(mpg ~ I(displacement^2) + I(horsepower^2) + I(weight^2), data = Auto)
summary(lm_square)

```

