---
title: "Ch.3 Hw Problem 10"
output: html_document
date: "2023-09-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages('ISLR')
library(ISLR)
```

```{r}
head(Carseats)
```


a.) Fit a multiple regression model to predict Sales using Price,
Urban, and US.

```{r}
#Fit the model 
model = lm(Sales ~ Price + Urban + US, data = Carseats)
summary(model)
```

b.) Provide an interpretation of each coefficient in the model. Be
careful—some of the variables in the model are qualitative!

```{r}

```

c.) Write out the model in equation form, being careful to handle the qualitative variables properly.

```{r}

```

d.) For which of the predictors can you reject the null hypothesis H0 :βj =0?

```{r}
summary(model)
```

(e) On the basis of your response to the previous question, fit a smaller model that only uses the predictors for which there is evidence of association with the outcome.

```{r}
smaller_model = lm(Sales ~ Price + US, data = Carseats)
summary(smaller_model)
```



(f) How well do the models in (a) and (e) fit the data?
```{r}

```


(g) Using the model from (e), obtain 95% confidence intervals for the coefficient(s).
```{r}
confint(smaller_model, level = 0.95)

```

(h) Is there evidence of outliers or high leverage observations in the model from (e)?
```{r}
#diagnostic plots
par(mfrow=c(2,2))
plot(smaller_model)

```